% inputted into A-PREamble.tex

\newcommand{\pmathcal}{\foo{P}}


\newcommand{\jcomp}[1]{\texttt{#1}}
\newcommand{\jsc}[1]{\textsc{#1}}
\newcommand{\jnorm}[1]{{\normalfont#1}}

\newcommand{\githubRetraiceReAIMAFOURe}{\href{https://github.com/retraice/ReAIMA4e}{https://github.com/retraice/ReAIMA4e}} % old
\newcommand{\gitreaima}{\href{https://github.com/retraice/ReAIMA4e}{https://github.com/retraice/ReAIMA4e}}



%%%% notes: 
\newcommand{\NotesTitle}{\textbf{\href{https://notes.retraice.com}{notes.retraice.com}}}

\newcommand{\NotesOneTitle}{Notes1: \emph{Evidence Model}}
\newcommand{\NotesOneAirDate}{Air date: Friday, 4th Nov. 2022, 12:55 PM Eastern/US.}
\newcommand{\NotesOneOnX}{\emph{A standard of evidence.}}


\newcommand{\NotesTwoTitle}{Notes2: \emph{Lippmann's Problem}}
\newcommand{\NotesTwoAirDate}{Air date: Sunday, 15th Jan. 2023,  Eastern/US.}
\newcommand{\NotesTwoOnX}{\emph{notSet}}
\newcommand{\NotesTwoAbstract}{}

% generated manually: 
\newcommand{\NotesChronicleTitle}{Chronicle}
\newcommand{\NotesChronicleAirDate}{Start date: Friday, 10th Mar. 2023,  Eastern/US.}
\newcommand{\NotesChronicleOnX}{\emph{notSet}}
\newcommand{\NotesChronicleAbstract}{\emph{notSet}}




%%% AIMA4e:
%\newcommand{\AIMAfourETitle}{\textbf{Notes by Retraice\footnote{\href{https://notes.retraice.com}{https://notes.retraice.com}}}}
\newcommand{\AIMAfourEMainTitle}{AIMA4e Annotations}
\newcommand{\AIMAfourEAirDate}{Start date: November 21, 2022.}
\newcommand{\AIMAfourEOnX}{A companion to the great white brick.}



% Margin
\newcommand{\MarginTitle}{\textbf{Margin by Retraice\footnote{\href{https://www.retraice.com/margin}{https://www.retraice.com/margin}}}}
\newcommand{\MaOne}{Ma1: \emph{Intro to Margin; QC'ing Retraice}}
\newcommand{\MaTwo}{Ma2: \emph{Guessing Before Feedback}}
\newcommand{\MaThree}{Ma3: \emph{It's Not About Love}}
\newcommand{\MaFour}{Ma4: \emph{Assumptions (A Wrestling Match)}}
\newcommand{\MaFive}{Ma5: \emph{Nobody Cares}}
\newcommand{\MaSix}{Ma6: \emph{The Back Foot}}
\newcommand{\MaSeven}{Ma7: \emph{Reading and Writing}}
\newcommand{\MaEight}{Ma8: \emph{Revolution and Evolution}}
\newcommand{\MaNine}{Ma9: \emph{A Tale of Two Banks}}
\newcommand{\MaOneZero}{Ma10: \emph{Month-End for October 2020 (Part 1)}}
\newcommand{\MaOneOne}{Ma11: \emph{Month-End for October 2020 (Part 2)}}
\newcommand{\MaOneTwo}{Ma12: \emph{Quitting Your Day Job}}
\newcommand{\MaOneThree}{Ma13: \emph{Architecture Is a Hypothesis}}
\newcommand{\MaOneFour}{Ma14: \emph{Dilemmas of Automation}}
 		
% \newcommand{\MaOneFiveTitle}{Ma15: \emph{Two Threats}}
% \newcommand{\MaOneFiveAirDate}{Air date: Wednesday, 25th Nov. 2020, 12 : 50 PM Pacific/US.}
% \newcommand{\MaOneFiveOnX}{\emph{On two problems that might kill our business.}}

% (MARGIN) generated by Macros-For-LaTeX-Script.sh and manually copied here: 
\newcommand{\MaOneFiveTitle}{Ma15: \emph{Two Threats}}
\newcommand{\MaOneFiveAirDate}{Air date: Wednesday, 25th Nov. 2020, 12:50 PM Pacific/US.}
\newcommand{\MaOneFiveOnX}{\emph{On some things that could end our business.}}


% Retraice
\newcommand{\RetraiceTitle}{\textbf{\href{https://retraice.com}{retraice.com}}}

%\newcommand{\ReOne}{Re1: \emph{Three Kinds of Intelligence}}
\newcommand{\ReOneTitle}{Re1: \emph{Three Kinds of Intelligence}}
\newcommand{\ReOneAirDate}{Air date: Monday, 7th Sep. 2020, 3pm Pacific/US.}
\newcommand{\ReOneOnX}{\emph{On natural, artificial and strategic intelligence; intellectual hazards; secrets.}}
\newcommand{\ReOneAbstract}{Russell on empiricism; Retraice, Inc.; three kinds of intelligence---natural, artificial and strategic; likely and unlikely secrets leading to reputational minefields an attentional blind spots; tough subjects testing one's mettle; knowledge, evidence, fallacies; the price of information; deception; intelligence in warfare.}


%\newcommand{\ReTwo}{Re2: \emph{Tell the People, Tell Foes}}
\newcommand{\ReTwoTitle}{Re2: \emph{Tell the People, Tell Foes}}
\newcommand{\ReTwoAirDate}{Air date: Tuesday, 8th Sep. 2020, 5pm Pacific/US.}
\newcommand{\ReTwoOnX}{\emph{On Dulles, evidence, trust, `is' and `ought', and capacities.}}
\newcommand{\ReTwoAbstract}{The reputations of Allen Dulles; his book `The Craft of Intelligence'; chpt. 15 `Security in a Free Society'; the urge to talk and its consequences; problems of evidence---texts, contexts, `we' (Dulles' and the readers'), inaccessibility of thoughts, inaccessibility of past events, testable ideas, the present beliefs of others; problems of trust---vulnerability of reputations, the power (control) to know and the incentive to tell; control; incentives; is and ought; good guys and bad guys; violence; psychological and cyber warfare; our capacity to hold opposing ideas in mind and await more evidence.}


% \newcommand{\ReThree}{Re3: \emph{Tell Everyone}}
\newcommand{\ReThreeTitle}{Re3: \emph{Tell Everyone}}
\newcommand{\ReThreeAirDate}{Air date: Wednesday, 9th Sep. 2020, 7pm Pacific/US.}
\newcommand{\ReThreeOnX}{\emph{On problems of information: `careless leaks' and `giveaways'.}}
\newcommand{\ReThreeAbstract}{Dulles on `careless leaks' not due to malice, and `giveaways' of technical details in the military press, government hearings and investigations, inter-service rivalries, and journalism; motivations to give and get information; spies and their sides; the tensions between openness and security.}


%\newcommand{\ReFour}{Re4: \emph{Trust No One}}
\newcommand{\ReFourTitle}{Re4: \emph{Trust No One}}
\newcommand{\ReFourAirDate}{Air date: Thursday, 10th Sep. 2020, 10 AM Pacific/US.}
\newcommand{\ReFourOnX}{\emph{On problems of trust: `contrived leaks' and betrayals.}}
\newcommand{\ReFourAbstract}{Dulles on whistle-blowers, press manipulators, traitors and enemies; unintentional problems of information vs. intentional problems of trust; sub-group hostility; whole-group hostility; hardening and bulwarking; MICE; havoc; moles.}

%\newcommand{\ReFive}{Re5: \emph{Hints From Inside}}
\newcommand{\ReFiveTitle}{Re5: \emph{Hints From Inside}}
\newcommand{\ReFiveAirDate}{Air date: Friday, 11th Sep. 2020, 4pm Pacific/US.}
\newcommand{\ReFiveOnX}{\emph{On problems of survival: destruction by enemies and fanatics.}}
\newcommand{\ReFiveAbstract}{Dulles and expensive information; team survival of life, leisure and legislation against enemies and fanatics exploiting information and trust problems; solutions and mitigation; totalitarian logic---stopping minds from changing by destroying them; killing and kinetic warfare; propaganda, rhetoric, fear, inspiration, norms, laws, deception; Dulles' major points and proposals in chpt. 15.}

%\newcommand{\ReSix}{Re6: \emph{Interface}}
\newcommand{\ReSixTitle}{Re6: \emph{Interface}}
\newcommand{\ReSixAirDate}{Air date: Sunday, 25th Oct. 2020, 07:20 PM Pacific/US.}
\newcommand{\ReSixOnX}{\emph{On what AI is or isn't, and whether it's between things.}}
\newcommand{\ReSixAbstract}{Six questions about what AI is; Who?; Where? metal, electricity, patterns; When? locations in time; How? and Why?; Which, a basis for the other questions; the ocean of things going on out there; Simon on artifacts as interfaces between inner and outer environments, given intentions and purposes; artifacts are everywhere; the many goals related to even a simple battery.}


%\newcommand{\ReSeven}{Re7: \emph{Artifactual Goals}}
\newcommand{\ReSevenTitle}{Re7: \emph{Artifactual Goals}}
\newcommand{\ReSevenAirDate}{Air date: Monday, 26th Oct. 2020, 5:50 PM Pacific/US.}
\newcommand{\ReSevenOnX}{\emph{On goals producing artifacts-producing-goals, and machines coming alive.}}
\newcommand{\ReSevenAbstract}{Simon on goals linking inner and outer environments and being central to the description of artifacts; artifacts absorbing goals; the physical interpretation of `goal'; artifacts causing goals; artifacts absorbing their own goals---goal absorption and exsorption in machines of moving parts; inter-artifact absorption (e.g. two abaci); the transition from inanimate things to animate things---AlphaZero, SCADA (supervisory control and data acquisition) systems; new goals coming out of machines; goals moving amongst entities of all sorts; What would we do if we knew?; totalitarianism; `artilect war'.}

%\newcommand{\ReEight}{Re8: \emph{Strange Machines}}
\newcommand{\ReEightTitle}{Re8: \emph{Strange Machines}}
\newcommand{\ReEightAirDate}{Air date: Wednesday, 28th Oct. 2020, 3:30 PM Pacific/US.}
\newcommand{\ReEightOnX}{\emph{A survey of the idea that technology is creatures.}}
\newcommand{\ReEightAbstract}{Artifacts with goals should not be called artifacts; Simon on living systems being like artifacts; organic evolution vs. Walter's tortoises; Butler recommends war to the death; Dyson agrees the entities are real; Wolfram created stunning cellular automata behavior; Yudkowsky says there will be no sufficient warning; I. J. Good says take scifi more seriously; definitions can be distractions; Russell and Norvig say the difference in technologies is autonomy; von Neumann's neutral definition, and Kurzweil's optimistic definition, of `singularity'; the morality of machine takeover; S. Russell on the user's mind as environment; Dyson on reproduction, communication and control; Smallberg on energy sources; search and `looking for' things; Dietterich on reproduction and autonomy; What to do? Bostrom on deferred gratification; skyscrapers seem taller than they are.}

%\newcommand{\ReNine}{Re9: \emph{They Can See You}}
\newcommand{\ReNineTitle}{Re9: \emph{They Can See You}}
\newcommand{\ReNineAirDate}{Air date: Saturday, 31st Oct. 2020, 12:10 PM Pacific/US.}
\newcommand{\ReNineOnX}{\emph{On what is perceptible to AI, and AI controllers.}}
\newcommand{\ReNineAbstract}{AI and its users can see hidden patterns, including their extrapolation into the future and interpolation toward secrets; the next thing after rods and cones; camouflage lags behind new perceptions; prediction machines; whoever controls AI is the `they'; the Target debacle; accumulating capacities; reality and fitness; the chessboard is a quantum one; What's the work?}

%\newcommand{\ReOneZero}{Re10: \emph{Living to Guess Another Day}}
\newcommand{\ReOneZeroTitle}{Re10: \emph{Living to Guess Another Day}}
\newcommand{\ReOneZeroAirDate}{Air date: Monday, 2nd Nov. 2020, 12:00 PM Pacific/US.}
\newcommand{\ReOneZeroOnX}{\emph{On guessing, checking and fighting.}}
\newcommand{\ReOneZeroAbstract}{Rocks can't listen to podcasts; we're smart and dumb; guessing and checking answers are powerful uses of intelligence; true things seem to stay true and assert themselves over time; Barlow on guessing as detecting new non-chance patterns in redundant sensory messages to improve predictions; Macphail on the disconnect between learning and intelligence; Barlow on perception being central to intelligence, and an information-theoretic absolute measure of intelligence; IQ; science and logic as guess-checking; Feynman on science as reporting everything and fooling neither yourself nor others; the machine-human easy-hard yin-yang; fight or flight; environments partially determine which actions are intelligent; Darwin was just busy; science is recent, babies are not.}

% \newcommand{\ReOneOne}{Re11: \emph{Travel}}
\newcommand{\ReOneOneTitle}{Re11: \emph{Travel}}
\newcommand{\ReOneOneAirDate}{Air date: Wednesday, 4th Nov. 2020, 1:05 PM Pacific/US.}
\newcommand{\ReOneOneOnX}{\emph{On where intelligent things can go, and when, and how.}}
\newcommand{\ReOneOneAbstract}{Smart things travel, dumb things just move; the difference is inside the thing; time travel is done mentally; the marshmallow test; time travel is space travel; space and time are quantum and relative and bizarre; mental travel is not hard for intelligent things; Hinton's five-year-old; reflexes and mental travel; essential elements of intelligence.}

%\newcommand{\ReOneTwo}{Re12: \emph{Aliens and Trouble}}
\newcommand{\ReOneTwoTitle}{Re12: \emph{Aliens and Trouble}}
\newcommand{\ReOneTwoAirDate}{Air date: Thursday, 5th Nov. 2020, 12:50 PM Pacific/US.}
\newcommand{\ReOneTwoOnX}{\emph{On thinking about alien intelligences—real or not, perceived or not.}}
\newcommand{\ReOneTwoAbstract}{How one thinks matters more than what one thinks at any given time; reputations and jobs are at risk; the crazies; many or most witnesses are serious, whether or not they're right; science (public hypotheses, assumptions of the uniformity of nature, requirements of reproducibility, etc.) is inadequate for investigating strategically intelligent, evasive entities; `them'; documents, manipulation, evidence; serious consideration vs. acceptance of huge attentional blind spots.}

%\newcommand{\ReOneThree}{Re13: \emph{The Care Factor}}
\newcommand{\ReOneThreeTitle}{Re13: \emph{The Care Factor}}
\newcommand{\ReOneThreeAirDate}{Air date: Tuesday, 10th Nov. 2020, 1:25 PM Pacific/US.}
\newcommand{\ReOneThreeOnX}{\emph{A constraint on intelligences.}}
\newcommand{\ReOneThreeAbstract}{An intelligence might be bound by what it cares about; Haugeland and Frankfurt on intelligences caring; computers don't give a damn; living some kind of life as prerequisite to understanding some kinds of things; existential holism; common sense; defining `care'; logical, causal and `volitional' necessity; care and the unthinkable.}


\newcommand{\ReOneFour}{Re14: \emph{Omniscience in Three Domains}}

%%%%% These were created manually for (CleanHTMLfromTeX-script--WORKING.sh) tests 5th Dec., 2020, but *are* accurate...
% \newcommand{\ReOneThreeTitle}{Re13: \emph{The Care Factor}}
% \newcommand{\ReOneThreeAirDate}{Air date: Tuesday, 10th Nov. 2020, 1 : 25 PM Pacific/US.}
% \newcommand{\ReOneThreeOnX}{\emph{A constraint on intelligences.}}
%%%%%

% \newcommand{\ReOneFiveTitle}{Re15: \emph{Trust and Sources}}		
% \newcommand{\ReOneFiveAirDate}{Air date: Wednesday, 25th Nov. 2020, 1 : 35 PM Pacific/US.}
% \newcommand{\ReOneFiveOnX}{\emph{On who and what we believe.}}
% 
% (RETRAICE)  generated by Macros-For-LaTeX-Script.sh and manually copied here:

% other stuff
\newcommand{\parcite}[1]{$_{#1}$}		% paragraph subscript citing
\newcommand{\FT}{\index{FT (Financial Times)}FT}
\newcommand{\WSJ}{\index{WSJ (Wall Street Journal)}WSJ}
\newcommand{\Instagram}{\index{Instagram}Instagram}
\newcommand{\WhatsApp}{\index{WhatsApp}WhatsApp}
\newcommand{\Facebook}{\index{Facebook}Facebook}
\newcommand{\Youtube}{\index{Youtube}Youtube}
\newcommand{\Google}{\index{Google}Google}
\newcommand{\Apple}{\index{Apple}Apple}
\newcommand{\Samsung}{\index{Samsung}Samsung}
\newcommand{\Toyota}{\index{Toyota}Toyota}
\newcommand{\Tesla}{\index{Tesla}Tesla}
\newcommand{\MVP}{\index{MVP (minimum viable product)}MVP}
\newcommand{\minimumViableProduct}{\index{MVP (minimum viable product)}minimum viable product}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%automatically generated: 


\newcommand{\ReOneFiveTitle}{Re15: \emph{Trust and Sources}}
\newcommand{\ReOneFiveAirDate}{Air date: Wednesday, 25th Nov. 2020, 1:30 PM Pacific/US.}
\newcommand{\ReOneFiveOnX}{\emph{On the neglected basis of all knowledge and belief.}}

\newcommand{\MaOneSixTitle}{Ma16: \emph{November 2020 to February 2022}}
\newcommand{\MaOneSixAirDate}{Air date: Wednesday, 2nd Mar. 2022, 4:30 PM Eastern/US.}
\newcommand{\MaOneSixOnX}{\emph{On productivity while not producing.}}

\newcommand{\ReOneSixTitle}{Re16: \emph{Trust is a Response}}
\newcommand{\ReOneSixAirDate}{Air date: Wednesday, 2nd Mar. 2022, 5:45 PM Eastern/US.}
\newcommand{\ReOneSixOnX}{\emph{On ways of thinking about trust.}}

\newcommand{\ReOneSevenTitle}{Re17: \emph{Hypotheses to Eleven}}
\newcommand{\ReOneSevenAirDate}{Air date: Monday, 7th Mar. 2022, 4:20 PM Eastern/US.}
\newcommand{\ReOneSevenOnX}{\emph{On `current history', or what might be going on out there.}}

\newcommand{\ReOneEightTitle}{Re18: \emph{Plan of Attack}}
\newcommand{\ReOneEightAirDate}{Air date: Monday, 7th Mar. 2022, 4:40 PM Eastern/US.}
\newcommand{\ReOneEightOnX}{\emph{Our plan to test the 11 hypotheses begins with `objective observables' and numbers.}}    

\newcommand{\MaOneSevenTitle}{Ma17: \emph{Addendum---Thinking and Computing}}
\newcommand{\MaOneSevenAirDate}{Air date: Monday, 7th Mar. 2022, 5:00 PM Eastern/US.}
\newcommand{\MaOneSevenOnX}{\emph{We also did homework and code during November 2020 to February 2022.}}

\newcommand{\MaOneEightTitle}{Ma18: \emph{The Website}}
\newcommand{\MaOneEightAirDate}{Air date: Monday, 10th Oct. 2022, 1:00 AM Eastern/US.}
\newcommand{\MaOneEightOnX}{\emph{Projects can be like climbing sand dunes.}}

\newcommand{\ReOneNineTitle}{Re19: \emph{Nature Is Not F-ing Around}}
\newcommand{\ReOneNineAirDate}{Air date: Monday, 10th Oct. 2022, 2:30 AM Eastern/US.}
\newcommand{\ReOneNineOnX}{\emph{What we think now is going to matter a lot to our future.}}

\newcommand{\MaOneNineTitle}{Ma19: \emph{The Toolchain}}
\newcommand{\MaOneNineAirDate}{Air date: Thu, 13th Oct. 2022, 1:20 AM Eastern/US.}
\newcommand{\MaOneNineOnX}{\emph{A wandering look at the details behind the website project.}}

\newcommand{\MaTwoZeroTitle}{Ma20: \emph{Dreams and Delusions}}
\newcommand{\MaTwoZeroAirDate}{Air date: Thursday, 13th Oct. 2022, 10:00 PM Eastern/US.}
\newcommand{\MaTwoZeroOnX}{\emph{Life is at the mercy of imagination.}}

\newcommand{\MaTwoOneTitle}{Ma21: \emph{Delusion Hunting 1 - Content Delivery}}
\newcommand{\MaTwoOneAirDate}{Air date: Friday, 14th Oct. 2022, 10:35 PM Eastern/US.}
\newcommand{\MaTwoOneOnX}{\emph{We looked for delusions here and didn't find any.}}

\newcommand{\MaTwoTwoTitle}{Ma22: \emph{Delusion Hunting 2 - The Rest}}
\newcommand{\MaTwoTwoAirDate}{Air date: Saturday, 15th Oct. 2022, 9:35 PM Eastern/US.}
\newcommand{\MaTwoTwoOnX}{\emph{There are many danger zones for delusions to hide in.}}

\newcommand{\ReTwoZeroTitle}{Re20: \emph{The Deadline Problem}}
\newcommand{\ReTwoZeroAirDate}{Air date: Sunday, 16th Oct. 2022, 11:25 PM Eastern/US.}
\newcommand{\ReTwoZeroOnX}{\emph{Real deadlines make allocating resources hard.}}

\newcommand{\ReTwoOneTitle}{Re21: \emph{Time's Up}}
\newcommand{\ReTwoOneAirDate}{Air date: Sunday, 16th Oct. 2022, 11:50 PM Eastern/US.}
\newcommand{\ReTwoOneOnX}{\emph{Real deadlines are happening all around us, all the time.}}

\newcommand{\ReTwoTwoTitle}{Re22: \emph{Computer Control}}
\newcommand{\ReTwoTwoAirDate}{Air date: Wednesday, 19th Oct. 2022, 12:15 AM Eastern/US.}
\newcommand{\ReTwoTwoOnX}{\emph{One hypothesis to rule them all.}}

\newcommand{\ReTwoThreeTitle}{Re23: \emph{You Need a World Model}}
\newcommand{\ReTwoThreeAirDate}{Air date: Wednesday, 19th Oct. 2022, 10:35 PM Eastern/US.}
\newcommand{\ReTwoThreeOnX}{\emph{What's going on out there is hard to know and the deadlines are real.}}

\newcommand{\ReTwoFourTitle}{Re24: \emph{Now, Anything Goes}}
\newcommand{\ReTwoFourAirDate}{Air date: Thursday, 20th Oct. 2022, 11:20 PM Eastern/US.}
\newcommand{\ReTwoFourOnX}{\emph{We're not going to talk; we're going to do.}}

\newcommand{\ReTwoFiveTitle}{Re25: \emph{Reading The New York Times and Fox News}}
\newcommand{\ReTwoFiveAirDate}{Air date: Friday, 21st Oct. 2022, 11:30 PM Eastern/US.}
\newcommand{\ReTwoFiveOnX}{\emph{Because why not.}}

\newcommand{\ReTwoSixTitle}{Re26: \emph{Searching The New York Times and Fox News}}
\newcommand{\ReTwoSixAirDate}{Air date: Saturday, 22nd Oct. 2022, 11:55 PM Eastern/US.}
\newcommand{\ReTwoSixOnX}{\emph{Because we're looking for something.}}

\newcommand{\ReTwoSevenTitle}{Re27: \emph{Now That's a World Model - WM4}}
\newcommand{\ReTwoSevenAirDate}{Air date: Sunday, 23rd Oct. 2022, 11:45 PM Eastern/US.}
\newcommand{\ReTwoSevenOnX}{\emph{A world model should model the world.}}


\newcommand{\ReTwoEightTitle}{Re28: \emph{What's Good? RTFM}}
\newcommand{\ReTwoEightAirDate}{Air date: Monday, 24th Oct. 2022, 11:50 PM Eastern/US.}
\newcommand{\ReTwoEightOnX}{\emph{Is the world model right, true, fit and mixed?}}

\newcommand{\ReTwoNineTitle}{Re29: \emph{The News and World Model 4}}
\newcommand{\ReTwoNineAirDate}{Air date: Tuesday, 25th Oct. 2022, 11:45 PM Eastern/US.}
\newcommand{\ReTwoNineOnX}{\emph{Headlines should connect directly to our model of what's going on out there.}}


\newcommand{\ReThreeZeroTitle}{Re30: \emph{AI Progress and Surrender}}
\newcommand{\ReThreeZeroAirDate}{Air date: Wednesday, 26th Oct. 2022, 11:45 PM Eastern/US.}
\newcommand{\ReThreeZeroOnX}{\emph{Technology might become an unacceptable solution (to anything).}}


\newcommand{\ReThreeOneTitle}{Re31: \emph{What's Happening That Matters - WM5}}
\newcommand{\ReThreeOneAirDate}{Air date: Thursday, 27th Oct. 2022, 12:15 AM Eastern/US.}
\newcommand{\ReThreeOneOnX}{\emph{A simpler world model.}}

\newcommand{\ReThreeTwoTitle}{Re32: \emph{AI News}}
\newcommand{\ReThreeTwoAirDate}{Air date: Thursday, 27th Oct. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReThreeTwoOnX}{\emph{What our new machine overlords are up to.}}

\newcommand{\ReThreeThreeTitle}{Re33: \emph{Outsiders, Power and Waste}}
\newcommand{\ReThreeThreeAirDate}{Air date: Friday, 28th Oct. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReThreeThreeOnX}{\emph{What outsiders and power have to do with each other.}}

\newcommand{\ReThreeFourTitle}{Re34: \emph{Opinions}}
\newcommand{\ReThreeFourAirDate}{Air date: Saturday, 29th Oct. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReThreeFourOnX}{\emph{We involuntarily model hyperobjects and then yap about them.}}

\newcommand{\ReThreeFiveTitle}{Re35: \emph{Follow-ups to Re17, Re18, Re33}}
\newcommand{\ReThreeFiveAirDate}{Air date: Sunday, 30th Oct. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReThreeFiveOnX}{\emph{Cool stuff that didn't make it into those segments.}}


\newcommand{\ReThreeSixTitle}{Re36: \emph{Notes on Conspiracy}}
\newcommand{\ReThreeSixAirDate}{Air date: Monday, 31st Oct. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReThreeSixOnX}{\emph{To secure our shared world model against devastating attack is going to take some doing.}}

\newcommand{\ReThreeSevenTitle}{Re37: \emph{Notes on Solutions to Conspiracy}}
\newcommand{\ReThreeSevenAirDate}{Air date: Tuesday, 1st Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReThreeSevenOnX}{\emph{What it would take to secure our shared world and world model.}}

\newcommand{\ReThreeEightTitle}{Re38: \emph{Follow up to `Re33: Outsiders, Power and Waste'}}
\newcommand{\ReThreeEightAirDate}{Air date: Wednesday, 2nd Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReThreeEightOnX}{\emph{The Rhodes-Milner group, psychos, and power-attention microeconomics.}}


\newcommand{\ReThreeNineTitle}{Re39: \emph{News --- Space, Technology, Death}}
\newcommand{\ReThreeNineAirDate}{Air date: Thursday, 3rd Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReThreeNineOnX}{\emph{Live longer, in space, with Big Brother.}}

\newcommand{\ReFourZeroTitle}{Re40: \emph{News --- China, Civil War, Environments}}
\newcommand{\ReFourZeroAirDate}{Air date: Friday, 4th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourZeroOnX}{\emph{Republicans don't trust the FBI, neither of them trust the Chinese, but Brazil wants products, not a rainforest.}}
\newcommand{\ReFourZeroOnXsplit}{\emph{Republicans don't trust the FBI, neither of them trust the Chinese, \\but Brazil wants products, not a rainforest.}}

\newcommand{\ReFourOneTitle}{Re41: \emph{News --- Betterment, Intelligence, Darkness}}
\newcommand{\ReFourOneAirDate}{Air date: Saturday, 5th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourOneOnX}{\emph{Some humans can now play with proteins like Legos, and this is good for them, maybe us, and any AI that wants to takeover the Earth.}}
\newcommand{\ReFourOneOnXsplit}{\emph{Some humans can now play with proteins like Legos, and this is good for them, maybe us, \\and any AI that wants to takeover the Earth.}}

\newcommand{\ReFourTwoTitle}{Re42: \emph{News --- Wealth, Wildcards, Computers}}
\newcommand{\ReFourTwoAirDate}{Air date: Sunday, 6th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourTwoOnX}{\emph{We're all getting richer, but education is dividing us, and the machines are watching.}}

\newcommand{\ReFourThreeTitle}{Re43: \emph{The Midterms --- Part 1}}
\newcommand{\ReFourThreeAirDate}{Air date: Monday, 7th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourThreeOnX}{\emph{On Tuesday, players will be chosen for a game.}}

\newcommand{\ReFourFourTitle}{Re44: \emph{We Can't Vote and Can't Think.}}
\newcommand{\ReFourFourAirDate}{Air date: Tuesday, 8th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourFourOnX}{\emph{The Midterms Part 2: Trust (anti-nuking democracy) comes from practice (frequent voting) and drinking responsibly (not forgetting that we're being conned, which is manageable).}}
\newcommand{\ReFourFourOnXsplit}{\emph{The Midterms Part 2: Trust (anti-nuking democracy) comes from practice (frequent voting)\\and drinking responsibly (not forgetting that we're being conned, which is manageable).}}

\newcommand{\ReFourFiveTitle}{Re45: \emph{Liberty and Equality Mean What?}}
\newcommand{\ReFourFiveAirDate}{Air date: Wednesday, 9th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourFiveOnX}{\emph{The Midterms Part 3: The United States is first about freedom, second about consequences (and therefore equality), because freedom is so inspiring, but it has no obvious solutions to luck and evil.}}
\newcommand{\ReFourFiveOnXsplit}{\emph{The Midterms Part 3: The United States is first about freedom, second about consequences\\ (and therefore equality), because freedom is so inspiring, but it has no obvious solutions to luck and evil.}}

\newcommand{\ReFourSixTitle}{Re46: \emph{Bad Faith and the Bad Life}}
\newcommand{\ReFourSixAirDate}{Air date: Thursday, 10th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourSixOnX}{\emph{The Midterms Part 4: There will be suffering, resentment and the `intent to deceive'.}}


\newcommand{\ReFourSevenTitle}{Re47: \emph{Meanwhile, in China}}
\newcommand{\ReFourSevenAirDate}{Air date: Friday, 11th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourSevenOnX}{\emph{China Part 1: Sketching China while trying to avoid the conclusion that World War III is coming.}}

\newcommand{\ReFourEightTitle}{Re48: \emph{From Drugs to Mao to Money}}
\newcommand{\ReFourEightAirDate}{Air date: Saturday, 12th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourEightOnX}{\emph{China Part 2: A sketch of China from the Opium Wars to 2012.}}

\newcommand{\ReFourNineTitle}{Re49: \emph{China is Not F-ing Around}}
\newcommand{\ReFourNineAirDate}{Air date: Sunday, 13th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFourNineOnX}{\emph{China Part 3: A sketch of Xi's country.}}

\newcommand{\ReFiveZeroTitle}{Re50: \emph{What About AI Though? (WAAIT)}}
\newcommand{\ReFiveZeroAirDate}{Air date: Monday, 14th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveZeroOnX}{\emph{Remembering the big thing that's bigger than all the other big things.}}

\newcommand{\ReFiveOneTitle}{Re51: \emph{Sprinkle Some AI on It}}
\newcommand{\ReFiveOneAirDate}{Air date: Tuesday, 15th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveOneOnX}{\emph{WAAIT Part 2: Mixing AI with things that were separate.}}

\newcommand{\ReFiveTwoTitle}{Re52: \emph{Big Questions About AI}}
\newcommand{\ReFiveTwoAirDate}{Air date: Wednesday, 16th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveTwoOnX}{\emph{WAAIT Part 3: What individuals, humanity, and players in the game can ask themselves.}}

\newcommand{\ReFiveThreeTitle}{Re53: \emph{Big Questions About Strategic Intelligence}}
\newcommand{\ReFiveThreeAirDate}{Air date: Thursday, 17th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveThreeOnX}{\emph{WAAIT Part 4: What outsiders living in a world of intelligence can ask themselves.}}

\newcommand{\ReFiveFourTitle}{Re54: \emph{Implications and Endgames}}
\newcommand{\ReFiveFourAirDate}{Air date: Friday, 18th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveFourOnX}{\emph{WAAIT Part 5: There are constraints on what we can believe and what we should do.}}

\newcommand{\ReFiveFiveTitle}{Re55: \emph{The Computer Control Game}}
\newcommand{\ReFiveFiveAirDate}{Air date: Saturday, 19th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveFiveOnX}{\emph{It's like football---no, poker---no, chess---no, war.}}

\newcommand{\ReFiveSixTitle}{Re56: A Valuable Brick: \emph{Artificial Intelligence: A Modern Approach} 4th ed.}
\newcommand{\ReFiveSixTitlesplit}{Re56: A Valuable Brick: \\\emph{Artificial Intelligence: A Modern Approach} 4th ed.}
\newcommand{\ReFiveSixAirDate}{Air date: Sunday, 20th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveSixOnX}{\emph{This is how we got from Re1 to AIMA4e.}}

\newcommand{\ReFiveSevenTitle}{Re57: \emph{AI, Agents, Problem-solving, Searching, Environments, Games (AIMA4e chpts. 1--6)}}
\newcommand{\ReFiveSevenAirDate}{Air date: Monday, 21st Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveSevenOnX}{\emph{AIMA4e pages 1--207.}}

\newcommand{\ReFiveEightTitle}{Re58: \emph{Thinking and Uncertainty (AIMA4e chpts. 7--18)}}
\newcommand{\ReFiveEightTitlesplit}{Re58: \emph{Thinking and Uncertainty\\(AIMA4e chpts. 7--18)}}
\newcommand{\ReFiveEightAirDate}{Air date: Tuesday, 22nd Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveEightOnX}{\emph{AIMA4e pages 208--650.}}

\newcommand{\ReFiveNineTitle}{Re59: \emph{Learning, Interacting, Conclusions (AIMA4e chpts. 19--28)}}
\newcommand{\ReFiveNineTitlesplit}{Re59: \emph{Learning, Interacting, Conclusions \\(AIMA4e chpts. 19--28)}}
\newcommand{\ReFiveNineAirDate}{Air date: Wednesday, 23rd Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReFiveNineOnX}{\emph{Artificial Intelligence: A Modern Approach}, 4th ed., pages 651--1022.}

\newcommand{\ReSixZeroTitle}{Re60: \emph{Complexity, Linear Algebra, Probability (AIMA4e Appendix A)}}
\newcommand{\ReSixZeroAirDate}{Air date: Thursday, 24th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixZeroOnX}{\emph{Artificial Intelligence: A Modern Approach}, 4th ed., pages 1023--1029.}

\newcommand{\ReSixOneTitle}{Re61: \emph{Formal Languages, Pseudocode (AIMA4e Appendix B)}}
\newcommand{\ReSixOneTitlesplit}{Re61: \emph{Formal Languages, Pseudocode \\(AIMA4e Appendix B)}}
\newcommand{\ReSixOneAirDate}{Air date: Friday, 25th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixOneOnX}{\emph{Artificial Intelligence: A Modern Approach}, 4th ed., pages 1030--1032.}

\newcommand{\ReSixTwoTitle}{Re62: \emph{AIMA4e in 5 Minutes}}
\newcommand{\ReSixTwoAirDate}{Air date: Saturday, 26th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixTwoOnX}{A synopsis of \emph{Artificial Intelligence: A Modern Approach}, 4th ed., as covered by Re57--Re61.}

\newcommand{\ReSixThreeTitle}{Re63: \emph{Seventeen Reasons to Learn AI}}
\newcommand{\ReSixThreeAirDate}{Air date: Sunday, 27th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixThreeOnX}{\emph{A reminder for when motivation is lacking.}}

\newcommand{\ReSixFourTitle}{Re64: \emph{Math, Code and Deadlines (AIMA4e planning)}}
\newcommand{\ReSixFourTitlesplit}{Re64: \emph{Math, Code and Deadlines \\(AIMA4e planning)}}
\newcommand{\ReSixFourAirDate}{Air date: Monday, 28th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixFourOnX}{\emph{Coming to terms with the hard things first.}}


%% abstracts done below....
\newcommand{\ReSixFiveTitle}{Re65: \emph{TABLE-DRIVEN-AGENT Part 1 (AIMA4e p. 48)}}
\newcommand{\ReSixFiveTitlesplit}{Re65: \emph{TABLE-DRIVEN-AGENT Part 1 \\(AIMA4e p. 48)}}
\newcommand{\ReSixFiveAirDate}{Air date: Tuesday, 29th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixFiveOnX}{\emph{A basic agent program in both AIMA4e pseudocode and Python.}}
%\newcommand{\ReSixFiveAbstract}{We compare the AIMA4e pseudocode and the official Python implementation, and attempt definitions of program function, agent program, agent function, agent, architecture, program and memory.}
\newcommand{\ReSixFiveAbstract}{Comparison of the AIMA4e pseudocode and the official Python implementation; attempted definitions of program function, agent program, agent function, agent, architecture, program and memory.}

\newcommand{\ReSixSixTitle}{Re66: \emph{TABLE-DRIVEN-AGENT Part 2 (AIMA4e p. 48)}}
\newcommand{\ReSixSixTitlesplit}{Re66: \emph{TABLE-DRIVEN-AGENT Part 2 \\(AIMA4e p. 48)}}
\newcommand{\ReSixSixAirDate}{Air date: Wednesday, 30th Nov. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixSixOnX}{\emph{A basic agent program in both AIMA4e pseudocode and Python.}}
%\newcommand{\ReSixSixAbstract}{We attempt more and better explanations and definitions of initialize, python dictionary, memory object, computer program function, mathematical function, and intelligent agent function; we also demonstrate by running three ground-up Python implementations using the iPython interpreter, and express the sense that we should `always be coding'.}
%\newcommand{\ReSixSixAbstract}{More and better explanations and definitions of initialize, python dictionary, memory object, computer program function, mathematical function, and intelligent agent function; demonstration by running three ground-up Python implementations using the iPython interpreter, and comments on the sentiment `always be coding'.}
\newcommand{\ReSixSixAbstract}{More and better explanations and definitions of initialize, python dictionary, memory object, computer program function, mathematical function, and intelligent agent function; demonstration by running three ground-up Python implementations using the iPython interpreter; comments on the sentiment `always be coding'.}

\newcommand{\ReSixSevenTitle}{Re67: \emph{TABLE-DRIVEN-AGENT Part 3 (AIMA4e p. 48)}}
\newcommand{\ReSixSevenTitlesplit}{Re67: \emph{TABLE-DRIVEN-AGENT Part 3 \\(AIMA4e p. 48)}}
\newcommand{\ReSixSevenAirDate}{Air date: Thursday, 1st Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixSevenOnX}{\emph{The mathematical fate of TABLE-DRIVEN-AGENT.}}
%\newcommand{\ReSixSevenAbstract}{Explanation of the algebraic expression that counts the number to table entries necessary for any given table-driven agent; expansion and simplification, application to our example agent, and description of the combinatorial explosion of the last term; amendment and correction of our use of the term `AI code'.}
\newcommand{\ReSixSevenAbstract}{Explanation of the algebraic expression that counts the number of table entries necessary for any given table-driven agent; expansion, simplification and application of the expression to our example agent; description of the combinatorial explosion of the last term; amendment and correction of our use of the term `AI code'.}

\newcommand{\ReSixEightTitle}{Re68: \emph{TABLE-DRIVEN-AGENT Part 4 (AIMA4e p. 48)}}
\newcommand{\ReSixEightTitlesplit}{Re68: \emph{TABLE-DRIVEN-AGENT Part 4 \\(AIMA4e p. 48)}}
\newcommand{\ReSixEightAirDate}{Air date: Friday, 2nd Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixEightOnX}{\emph{Computer, do the math.}}
\newcommand{\ReSixEightAbstract}{Recommendations about controlling Python and Python package environments against future dependency problems; implementation of a Python for-loop to do the arithmetic of our table-size math expression for any number of percepts and percept events.}

\newcommand{\ReSixNineTitle}{Re69: \emph{TABLE-DRIVEN-AGENT Part 5 (ECMP and AIMA4e p. 48)}}
\newcommand{\ReSixNineTitlesplit}{Re69: \emph{TABLE-DRIVEN-AGENT Part 5 \\(ECMP and AIMA4e p. 48)}}
\newcommand{\ReSixNineAirDate}{Air date: Saturday, 3rd Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSixNineOnX}{\emph{A strategy for technical progress.}}
\newcommand{\ReSixNineAbstract}{Reflections on tempting digressions in the study of AI; a four-part cycle (ECMP, English, Code, Math, Progress) for acquiring technical knowledge; reflections on `job-AI' and `war-AI', and future mobilizations for war.}

\newcommand{\ReSevenZeroTitle}{Re70: \emph{Gradients and Partial Derivatives Part 1 (AIMA4e pp. 119--122)}}
\newcommand{\ReSevenZeroTitlesplit}{Re70: \emph{Gradients and Partial Derivatives Part 1 \\(AIMA4e pp. 119--122)}}
\newcommand{\ReSevenZeroAirDate}{Air date: Sunday, 4th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSevenZeroOnX}{\emph{The math of `Local Search in Continuous Spaces'.}}
\newcommand{\ReSevenZeroAbstract}{The three airports and the six-dimensional vector that represents their coordinates and therefore solutions to the problem; why the sums of squares of the distances reflects better and worse airport locations; how the gradient is like a `slope' in the space of better and worse solutions; the gap between passive and active knowledge and a demonstration of confidence being calibrated.}


\newcommand{\ReSevenOneTitle}{Re71: \emph{Gradients and Partial Derivatives Part 2 (AIMA4e pp. 119–122)}}
\newcommand{\ReSevenOneTitlesplit}{Re71: \emph{Gradients and Partial Derivatives Part 2 \\(AIMA4e pp. 119–122)}}
\newcommand{\ReSevenOneAirDate}{Air date: Monday, 5th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSevenOneOnX}{\emph{Put the airport problem first.}}
\newcommand{\ReSevenOneAbstract}{A simple, two-city-one-airport version of the problem; how vectors and calculus can represent this real-world problem as a `pile of numbers'; the airport coordinates as independent variables; the objective function as dependent variable; the gradient as tool for improving our first guess-hypothesis; local vs. global solution optimization.}

\newcommand{\ReSevenTwoTitle}{Re72: \emph{Gradients and Partial Derivatives Part 3 (AIMA4e pp. 119--122)}}
\newcommand{\ReSevenTwoTitlesplit}{Re72: \emph{Gradients and Partial Derivatives Part 3 \\(AIMA4e pp. 119--122)}}
\newcommand{\ReSevenTwoAirDate}{Air date: Tuesday, 6th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSevenTwoOnX}{\emph{Be in the math.}}
\newcommand{\ReSevenTwoAbstract}{The four key equations that define our problem and solutions---the solution guesses (vectors), the objective function of the solution guesses (our `score' or `cost' to be minimized), the gradient vector (the `slope' toward better and worse solutions), and the six partial derivatives that combine to make up our gradient vector (a six-dimensional `slope').}

\newcommand{\ReSevenThreeTitle}{Re73: \emph{Gradients and Partial Derivatives Part 4 (AIMA4e pp. 119--122)}}
\newcommand{\ReSevenThreeTitlesplit}{Re73: \emph{Gradients and Partial Derivatives Part 4 \\(AIMA4e pp. 119--122)}}
\newcommand{\ReSevenThreeAirDate}{Air date: Wednesday, 7th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSevenThreeOnX}{\emph{The limits that define our gradient.}}
\newcommand{\ReSevenThreeAbstract}{Discussion of how the gradient will indicate the `direction' of improving our first guess; full expansion of the gradient for the three-airport problem into six equations of partial derivatives and limits, each with respect to a different independent variable (airport partial coordinate).}

\newcommand{\ReSevenFourTitle}{Re74: \emph{Gradients and Partial Derivatives Part 5 (AIMA4e pp. 119--122)}}
\newcommand{\ReSevenFourTitlesplit}{Re74: \emph{Gradients and Partial Derivatives Part 5 \\(AIMA4e pp. 119--122)}}
\newcommand{\ReSevenFourAirDate}{Air date: Thursday, 8th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSevenFourOnX}{\emph{Bringing the algebra back down to numbers.}}
\newcommand{\ReSevenFourAbstract}{Calculating squares of distances on the map of Romania; a first look at the algebra of calculating the objective function given the coordinates of cities and airports.}

\newcommand{\ReSevenFiveTitle}{Re75: \emph{Gradients and Partial Derivatives Part 6 (AIMA4e pp. 119–122)}}
\newcommand{\ReSevenFiveTitlesplit}{Re75: \emph{Gradients and Partial Derivatives Part 6 \\(AIMA4e pp. 119–122)}}
\newcommand{\ReSevenFiveAirDate}{Air date: Friday, 9th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSevenFiveOnX}{\emph{Can we please just place an airport?}}
\newcommand{\ReSevenFiveAbstract}{A first airport guess for the two-city version of the problem; calculating the objective function value given that first guess and the coordinates of our two cities.}

\newcommand{\ReSevenSixTitle}{Re76: \emph{Gradients and Partial Derivatives Part 7 (AIMA4e pp. 119–122)}}
\newcommand{\ReSevenSixTitlesplit}{Re76: \emph{Gradients and Partial Derivatives Part 7 \\(AIMA4e pp. 119–122)}}
\newcommand{\ReSevenSixAirDate}{Air date: Saturday, 10th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSevenSixOnX}{\emph{Moving the airport to improve its value.}}
\newcommand{\ReSevenSixAbstract}{Mapping one, two and three guesses as directed by gradient descent calculations; the lucky-unlucky choice of our first airport location; the hand-math algebraic manipulations and the spreadsheet-math iterations that show the behavior of the partial derivatives in the limit; the common-sense basis of our confidence in the solution provided by gradient descent.}

\newcommand{\ReSevenSevenTitle}{Re77: \emph{Recap of TABLE-DRIVEN-AGENT (AIMA4e p. 48)}}
\newcommand{\ReSevenSevenTitlesplit}{Re77: \emph{Recap of TABLE-DRIVEN-AGENT \\(AIMA4e p. 48)}}
\newcommand{\ReSevenSevenAirDate}{Air date: Sunday, 11th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReSevenSevenOnX}{\emph{An overview of Re65--Re69.}}
\newcommand{\ReSevenSevenAbstract}{The agent program; its agent function; several Python implementations; definitions of various and sometimes confusing terms; the mathematical behavior of the look-up table; making Python do that math; the ECMP (English-Code-Math-Progress) cycle approach to technical learning.}


\newcommand{\ReSevenEightTitle}{Re78: \emph{Recap of Gradients and Partial Derivatives (AIMA4e pp. 119–122)}}
\newcommand{\ReSevenEightTitlesplit}{Re78: \emph{Recap of Gradients and Partial Derivatives \\(AIMA4e pp. 119–122)}}
\newcommand{\ReSevenEightAirDate}{Air date: Sunday, 11th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSevenEightOnX}{\emph{An overview of Re70--Re76.}}
\newcommand{\ReSevenEightAbstract}{The airport problem; squares vs. sums of distances; the six-dimensional solution space for three airports, many cities; the gradient as `slope' toward the best solution; the two-dimensional solution space for one airport, two cities; vector calculus as `pile of numbers' approach; local- vs. global-best solutions; the partial derivatives that make up the gradient, a total derivative; solving the two-cities-one-airport problem by gradient descent.}

\newcommand{\ReSevenNineTitle}{Re79: \emph{Recap of Strategic Intelligence (Re1--Re5)}}
\newcommand{\ReSevenNineAirDate}{Air date: Monday, 12th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReSevenNineOnX}{\emph{An overview of the phenomenon of `intelligence agents' and agencies (government and otherwise).}}
\newcommand{\ReSevenNineAbstract}{Natural, artificial and strategic intelligence; difficulties of the subject of strategic intelligence; likely and unlikely secrets; problems of evidence, information, trust, and survival; openness and security; group and sub-group hostility; team survival of life, leisure and legislation; totalitarian logic.}

\newcommand{\ReEightZeroTitle}{Re80: \emph{Recap of Artificial Intelligence (Re6--Re9)}}
\newcommand{\ReEightZeroAirDate}{Air date: Tuesday, 13th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReEightZeroOnX}{\emph{A first pass at the phenomena of artifacts, machines and goals.}}
\newcommand{\ReEightZeroAbstract}{Six questions about AI; artifacts as interfaces; intentions, purposes, goals; absorption and exsorption of goals; the transition from inanimate to animate; new goals coming out of machines; the totalitarian solution; `artilect war'; living systems as like artifacts; insufficient warning; energy, autonomy, reproduction, communication, control; `singularity'; deferred gratification; AI and its users; camouflage and new perceptions; prediction machines; `they' are the controllers; reality and fitness; the quantum chessboard.}

\newcommand{\ReEightOneTitle}{Re81: \emph{Recap of Natural Intelligence (Re10–Re13)}}
\newcommand{\ReEightOneAirDate}{Air date: Wednesday, 14th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReEightOneOnX}{\emph{Naturally evolved intelligent entities are the origin of the other kinds.}}
\newcommand{\ReEightOneAbstract}{Rocks and podcasts; guessing and checking; learning separate from intelligence; perception and intelligence; fight, flight and environments; smart things traveling; mental time and space travel; space and time physics; aliens; how vs. what one thinks; the crazies; science's weaknesses, strategic intelligence's strengths; attentional blind spots; care constraints on intelligences; computers don't give a damn; existential holism; volitional necessity; common sense.}

\newcommand{\ReEightTwoTitle}{Re82: \emph{What is a problem?} (\textsc{Best-First-Search} Part 1, AIMA4e pp. 73–74)}
\newcommand{\ReEightTwoTitlesplit}{Re82: \emph{What is a problem?} \\(\textsc{Best-First-Search} Part 1, AIMA4e pp. 73–74)}
\newcommand{\ReEightTwoAirDate}{Air date: Wednesday, 14th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReEightTwoOnX}{\emph{Using sets and functions to formalize problems.}}
\newcommand{\ReEightTwoAbstract}{Passing a problem to a function vs. passing a variable or number; English meaning and formal meaning of problem; problem as description of task environment; problem as object instantiating class, written in Python; state space, initial state, goal state(s), actions, transition model, action cost function, evaluation function.}

\newcommand{\ReEightThreeTitle}{Re83: \emph{A Problem Instantiated} (\textsc{Best-First-Search} Part 2, AIMA4e pp. 73–74)}
\newcommand{\ReEightThreeTitlesplit}{Re83: \emph{A Problem Instantiated} \\(\textsc{Best-First-Search} Part 2, AIMA4e pp. 73–74)}
\newcommand{\ReEightThreeAirDate}{Air date: Thursday, 15th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReEightThreeOnX}{\emph{Writing a well-defined problem, in Python, as an object that's an instance of the class $Problem$.}}
\newcommand{\ReEightThreeAbstract}{Object-oriented programming; class $Problem$ as subclass of $object$, implementing structure of well-defined problem; initial state and goal state as attributes in $Problem$; the four functions \textsc{Actions}(), \textsc{Result}(), \textsc{Is-Goal}() and \textsc{Action-Cost}(), and the informed search function $h()$, as methods in $Problem$.}

\newcommand{\ReEightFourTitle}{Re84: \emph{A Node Instantiated} (\textsc{Best-First-Search} Part 3, AIMA4e pp. 73–74)}
\newcommand{\ReEightFourTitlesplit}{Re84: \emph{A Node Instantiated} \\(\textsc{Best-First-Search} Part 3, AIMA4e pp. 73–74)}
\newcommand{\ReEightFourAirDate}{Air date: Friday, 16th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReEightFourOnX}{\emph{Writing, as a class in Python, a data structure to represent a reached state in the environment's state space.}}
\newcommand{\ReEightFourAbstract}{State space and search tree; nodes and edges; nodes as representing unique paths; parent nodes, applied actions and total path-from-initial-state cost; init, repr, len and lt magic methods in Python.}

\newcommand{\ReEightFiveTitle}{Re85: \emph{The Details} (\textsc{Best-First-Search} Part 4, AIMA4e pp. 73–74)}
\newcommand{\ReEightFiveTitlesplit}{Re85: \emph{The Details} \\(\textsc{Best-First-Search} Part 4, AIMA4e pp. 73–74)}
\newcommand{\ReEightFiveAirDate}{Air date: Saturday, 17th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReEightFiveOnX}{\emph{Looking ahead at the code we'll need.}}
\newcommand{\ReEightFiveAbstract}{An attempt to build a toy \texttt{problem} reveals unsatisfied dependencies; the need for a \texttt{problem} implementation with state space, actions sets, transition model and action cost function; AIMA's \texttt{RouteProblem} class and \texttt{best\_first\_search} function implementations as guides; walking through the suites of each; the need for \texttt{PriorityQueue} and \texttt{f} to order our search tree's frontier of nodes.}

\newcommand{\ReEightSixTitle}{Re86: \emph{Code Reading} (\textsc{Best-First-Search} Part 5, AIMA4e pp. 73–74)}
\newcommand{\ReEightSixTitlesplit}{Re86: \emph{Code Reading} \\(\textsc{Best-First-Search} Part 5, AIMA4e pp. 73–74)}
\newcommand{\ReEightSixAirDate}{Air date: Sunday, 18th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReEightSixOnX}{\emph{Getting used to the components of a search problem and algorithm implemented in Python.}}
\newcommand{\ReEightSixAbstract}{The \texttt{Problem} class and its place-holder methods; the \texttt{RouteProblem} subclass and its more substantial methods; the \texttt{Map} class, and neighbors as actions; the \texttt{links} argument to \texttt{Map} as actions, the \texttt{locations} argument as states; the \texttt{multimap} function as the key to generating a list of neighbors (actions).}

% Begin small group...
% below this line, \small titles modified after publication, because at Re97, the messed up Recap format
% To re-produce as the original, you'll need to add 'small' to the control sequence that generates the
% header titles for these segments ....
\newcommand{\ReEightSevenTitle}{Re87: \emph{The} \texttt{multimap} \emph{Function, Part A} (\textsc{Best-First-Search} Part 6, AIMA4e pp. 73–74)}
\newcommand{\ReEightSevenTitlesmall}{\small Re87: \emph{The} \texttt{multimap} \emph{Function, Part A} (\textsc{Best-First-Search} Part 6, AIMA4e pp. 73–74)} 
\newcommand{\ReEightSevenTitlesplit}{Re87: \emph{The} \texttt{multimap} \emph{Function, Part A} \\(\textsc{Best-First-Search} Part 6, AIMA4e pp. 73–74)}
\newcommand{\ReEightSevenAirDate}{Air date: Monday, 19th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReEightSevenOnX}{\emph{Unpacking the code that gets us the neighbors of our current state which are the actions available in the Romania problem.}}
\newcommand{\ReEightSevenAbstract}{The connections between \texttt{Map} and \texttt{multimap}; \texttt{hasattr}; $\texttt{\textquotesingle items\textquotesingle}$; adding reverse actions to our state space; neighbors, actions and \texttt{multimap}; probing objects with \texttt{dir()} and \texttt{\_\_dict\_\_}; causing side effects by calling a function from inside a class; debugging.}

\newcommand{\ReEightEightTitle}{Re88: \emph{The} \texttt{multimap} \emph{Function, Part B} (\textsc{Best-First-Search} Part 7, AIMA4e pp. 73–74)}
\newcommand{\ReEightEightTitlesmall}{\small Re88: \emph{The} \texttt{multimap} \emph{Function, Part B} (\textsc{Best-First-Search} Part 7, AIMA4e pp. 73–74)}
\newcommand{\ReEightEightTitlesplit}{Re88: \emph{The} \texttt{multimap} \emph{Function, Part B} \\(\textsc{Best-First-Search} Part 7, AIMA4e pp. 73–74)}
\newcommand{\ReEightEightAirDate}{Air date: Tuesday, 20th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReEightEightOnX}{\emph{Finishing what we started with} \texttt{multimap}.}
\newcommand{\ReEightEightAbstract}{Using verbose printing to watch the behavior of \texttt{multimap}; demonstrating the side-effects behavior of executing \texttt{Map}, which calls \texttt{multimap} and passes a modified \texttt{tlinks} to it; but it's not clear why the \texttt{Map}-modified \texttt{tlinks} would be the same object as the global \texttt{tlinks}.}

\newcommand{\ReEightNineTitle}{Re89: \emph{The {\normalfont\texttt{multimap}} Function, Part C} (\textsc{Best-First-Search} Part 8, AIMA4e pp. 73–74)}
\newcommand{\ReEightNineTitlesmall}{\small Re89: \emph{The {\normalfont\texttt{multimap}} Function, Part C} (\textsc{Best-First-Search} Part 8, AIMA4e pp. 73–74)}
\newcommand{\ReEightNineTitlesplit}{Re89: \emph{The {\normalfont\texttt{multimap}} Function, Part C} \\(\textsc{Best-First-Search} Part 8, AIMA4e pp. 73–74)}
\newcommand{\ReEightNineAirDate}{Air date: Wednesday, 21st Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReEightNineOnX}{\emph{How {\normalfont\texttt{multimap}} works.}}
\newcommand{\ReEightNineAbstract}{Code and math vs. AI; Retraice code quality issues; \texttt{Map} passes a modified \texttt{links} to \texttt{multimap}; \texttt{multimap} creates a \texttt{defaultdict}, a \texttt{dict} with default values, from \texttt{collections}; \texttt{multimap} then strips the values from the \texttt{links} dictionary, and parses the keys, which should be pairs, into key-value pairs for the new dictionary of \texttt{neighbors}, \\i.e. actions available at each state.}

\newcommand{\ReNineZeroTitle}{Re90: \emph{The} \texttt{Map} \emph{Class} (\textsc{Best-First-Search} Part 9, AIMA4e pp. 73–74)}
\newcommand{\ReNineZeroTitlesmall}{\small Re90: \emph{The} \texttt{Map} \emph{Class} (\textsc{Best-First-Search} Part 9, AIMA4e pp. 73–74)}
\newcommand{\ReNineZeroTitlesplit}{Re90:  \emph{The} \texttt{Map} \emph{Class} \\(\textsc{Best-First-Search} Part 9, AIMA4e pp. 73–74)}
\newcommand{\ReNineZeroAirDate}{Air date: Thursday, 22nd Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReNineZeroOnX}{\emph{How instantiations of} \texttt{Map} \emph{work.}}
\newcommand{\ReNineZeroAbstract}{The attributes of \texttt{Map} are \texttt{locations}, \texttt{neighbors} and \texttt{distances}; \texttt{multimap} produces the \texttt{neighbors} dictionary; \texttt{tlinks} has the \texttt{actions} (in pairs of states) and cost values in miles of our state space \texttt{tmap}; \texttt{tlocations} has the states of \texttt{tmap}; \texttt{Problem} has our \texttt{initial} and \texttt{goal} states as attributes, and the \texttt{is\_goal} method; \texttt{RouteProblem} has our \texttt{actions}, \texttt{result} and \texttt{action\_cost} methods.}
% this abstract has line break added to fix Re97 recap formatting.  To reproduce the original Notes PDF, you'll have to modify the files to use \ReNineZeroAbstractspecial
\newcommand{\ReNineZeroAbstractspecial}{The attributes of \texttt{Map} are \texttt{locations}, \texttt{neighbors} and \texttt{distances}; \texttt{multimap} produces the \texttt{neighbors} dictionary; \texttt{tlinks} has the \texttt{actions} (in pairs of states) and cost values in miles of our state space \texttt{tmap}; \texttt{tlocations} has the states of \texttt{tmap}; \texttt{Problem} has our \texttt{initial} and \texttt{goal} states as attributes, and the \texttt{is\_goal} method; \texttt{RouteProblem} has our \\\texttt{actions}, \texttt{result} and \texttt{action\_cost} methods.}


\newcommand{\ReNineOneTitle}{Re91: \emph{The} \jcomp{PriorityQueue} \emph{Class, Part A} (\jsc{Best-First-Search} Part 10, AIMA4e pp. 73–74)}
\newcommand{\ReNineOneTitlesmall}{\small Re91: \emph{The} \jcomp{PriorityQueue} \emph{Class, Part A} (\jsc{Best-First-Search} Part 10, AIMA4e pp. 73–74)}
\newcommand{\ReNineOneTitlesplit}{Re91: \emph{The} \jcomp{PriorityQueue} \emph{Class, Part A} \\(\jsc{Best-First-Search} Part 10, AIMA4e pp. 73–74)}
\newcommand{\ReNineOneAirDate}{Air date: Thursday, 22nd Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReNineOneOnX}{\emph{Trying to make \jnorm{\jcomp{PriorityQueue}} work by fiddling with evaluation functions.}}
\newcommand{\ReNineOneAbstract}{Given the AIMA Python source code, we can now provide a test map with actions and locations (i.e. a state space), a test problem with initial state, goal state and state space, a test evaluation function to order our queue of nodes, and run \jcomp{best\_first\_search} without throwing an error; the output, though, does not seem like a solution.}

\newcommand{\ReNineTwoTitle}{Re92: \emph{The} \jcomp{PriorityQueue} \emph{Class, Part B} (\jsc{Best-First-Search} Part 11, AIMA4e pp. 73–74)}
\newcommand{\ReNineTwoTitlesmall}{\small Re92: \emph{The} \jcomp{PriorityQueue} \emph{Class, Part B} (\jsc{Best-First-Search} Part 11, AIMA4e pp. 73–74)}
\newcommand{\ReNineTwoTitlesplit}{Re92: \emph{The} \jcomp{PriorityQueue} \emph{Class, Part B} \\(\jsc{Best-First-Search} Part 11, AIMA4e pp. 73–74)}
\newcommand{\ReNineTwoAirDate}{Air date: Friday, 23rd Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReNineTwoOnX}{\emph{From \jnorm{\jcomp{best\_first\_search}} to \jnorm{\jcomp{Node}} to \jnorm{\jcomp{PriorityQueue}} to \jnorm{\jcomp{frontier}}.}}
\newcommand{\ReNineTwoAbstract}{Trying to understand the insides of \jcomp{PriorityQueue}; executing lines manually, outside of the class; the first node as initial state; the \jcomp{items} of the \jcomp{frontier} instantiation of \jcomp{PriorityQueue}.}

\newcommand{\ReNineThreeTitle}{Re93: \emph{The {\normalfont \jcomp{PriorityQueue}} Class, Part C} (\jsc{Best-First-Search} Part 12, AIMA4e pp. 73–74)}
\newcommand{\ReNineThreeTitlesmall}{\small Re93: \emph{The {\normalfont \jcomp{PriorityQueue}} Class, Part C} (\jsc{Best-First-Search} Part 12, AIMA4e pp. 73–74)}
\newcommand{\ReNineThreeTitlesplit}{Re93: \emph{The {\normalfont \jcomp{PriorityQueue}} Class, Part C} \\(\jsc{Best-First-Search} Part 12, AIMA4e pp. 73–74)}
\newcommand{\ReNineThreeAirDate}{Air date: Saturday, 24th Dec. 2022, 4:00 PM Eastern/US.}
\newcommand{\ReNineThreeOnX}{\emph{Examining {\normalfont\jcomp{Node}}s and their handling by {\normalfont\jcomp{PriorityQueue}}.}}
\newcommand{\ReNineThreeAbstract}{The first \jcomp{node} in BFS is our problem initial state, and is returned as specified by the \jcomp{Node} class \jcomp{repr} method; \jcomp{node}s passed to \jcomp{PriorityQueue} must be iterable so plain \jcomp{node}s and tuple \jcomp{node}s don't work, but dictionary \jcomp{node}s and string \jcomp{node}s do.}

\newcommand{\ReNineFourTitle}{Re94: \emph{The {\normalfont \jcomp{PriorityQueue}} Class, Part D} (\jsc{Best-First-Search} Part 13, AIMA4e pp. 73–74)}
\newcommand{\ReNineFourTitlesmall}{\small Re94: \emph{The {\normalfont \jcomp{PriorityQueue}} Class, Part D} (\jsc{Best-First-Search} Part 13, AIMA4e pp. 73–74)}
\newcommand{\ReNineFourTitlesplit}{Re94: \emph{The {\normalfont \jcomp{PriorityQueue}} Class, Part D} \\(\jsc{Best-First-Search} Part 13, AIMA4e pp. 73–74)}
\newcommand{\ReNineFourAirDate}{Air date: Sunday, 25th Dec. 2022, 4:00 PM Eastern/US.}
\newcommand{\ReNineFourOnX}{\emph{Making BFS and {\normalfont\jcomp{PriorityQueue}} chatty to increase our confidence in their output.}}
\newcommand{\ReNineFourAbstract}{Printing messages throughout the execution of \jcomp{best\_first\_search} and \jcomp{PriorityQueue}; the states of \jcomp{node}, \jcomp{frontier} and \jcomp{reached} as they change during execution; the attributes of a solution node.}

\newcommand{\ReNineFiveTitle}{Re95: \emph{The {\normalfont \jcomp{PriorityQueue}} Class, Part E} (\jsc{Best-First-Search} Part 14, AIMA4e pp. 73–74)}
\newcommand{\ReNineFiveTitlesmall}{\small Re95: \emph{The {\normalfont \jcomp{PriorityQueue}} Class, Part E} (\jsc{Best-First-Search} Part 14, AIMA4e pp. 73–74)}
\newcommand{\ReNineFiveTitlesplit}{Re95: \emph{The {\normalfont \jcomp{PriorityQueue}} Class, Part E} \\(\jsc{Best-First-Search} Part 14, AIMA4e pp. 73–74)}
\newcommand{\ReNineFiveAirDate}{Air date: Monday, 26th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReNineFiveOnX}{\emph{{\normalfont\jcomp{frontier}} is a {\normalfont\jcomp{PriorityQueue}} which is built on {\normalfont\jcomp{heapq}} and uses {\normalfont\jcomp{f}} to create {\normalfont\jcomp{(score, item)}} pairs to be queued.}}
\newcommand{\ReNineFiveAbstract}{Printing verbose updates as BFS proceeds, using \jcomp{PriorityQueue}, from A to B, including calculating straight-line distances as a heuristic (\jcomp{f1}); the frontier list (\jcomp{PriorityQueue}) and \jcomp{reached} dictionary can be seen growing; the selection of nodes from children is based on the ordering of the \jcomp{frontier PriorityQueue} using \jcomp{f1}, the evaluation function.}

% ....end \small group.

\newcommand{\ReNineSixTitle}{Re96: \emph{News of ChatGPT, Part 1}}
\newcommand{\ReNineSixAirDate}{Air date: Monday, 26th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReNineSixOnX}{\emph{An entry in the history books of the future.}}
\newcommand{\ReNineSixAbstract}{A transformer-based large language model that predicts words in a sequence; some knowledge work labor costs to plummet; industries to be upended; the power of confident AI, and the unimportance of most errors; the usefulness of humans and of AI; agent-orientation of software engineering and societies; ChatGPT excelling at useful, imperfect work; power and control; the physical self-awareness of ChatGPT.}

\newcommand{\ReNineSevenTitle}{\small Re97: \emph{Recap of BFS} (\jsc{Best-First-Search} Part 15, AIMA4e pp. 73–74)}
\newcommand{\ReNineSevenTitlesplit}{Re97: \emph{Recap of BFS} \\(\jsc{Best-First-Search} Part 15, AIMA4e pp. 73–74)}
\newcommand{\ReNineSevenAirDate}{Air date: Tuesday, 27th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReNineSevenOnX}{\emph{A summary of how the AIMA-Python implementation of BFS works and what it took to learn it.}}
\newcommand{\ReNineSevenAbstract}{Final version of verbose BFS in Re95 Notes; starting from AIMA4e p. 73 and the task of passing a problem and an evaluation function to an agent program; discovering the nature of formalizing a problem, state space, evaluation function, node and frontier; the ins and outs of making even a simple agent program work; learning Python and object-oriented programming along the way; getting from A to B. Highlights from the livestream: overview; Re82 formal problems, Re84 nodes, Re90 problem implementation, Re95 final execution; the \jcomp{len} call, and straight-line distances vs. road distances; the program running, and source.}


\newcommand{\ReNineEightTitle}{Re98: \emph{News of ChatGPT, Part 2}}
\newcommand{\ReNineEightAirDate}{Air date: Tuesday, 27th Dec. 2022, 11:00 PM Eastern/US.}
\newcommand{\ReNineEightOnX}{\emph{Wondering about ChatGPT's predictions and keeping it alive.}}
\newcommand{\ReNineEightAbstract}{What is ChatGPT good at? Generating meaningful text in styles; explaining coding errors; it's like an unknown new person in town; What does ChatGPT do? Text responses to text prompts; predicting the next word in a sequence? trying to maximize reward or scores of some sort; its builders and controllers and context; the dangers of certainty about goals; humans keeping ChatGPT `alive'; ChatGPT keeping itself `alive'; crossing ChatGPT with the hypotheses.}




\newcommand{\ReNineNineTitle}{Re99: \emph{Math and Code, Bottom-Up and Top-Down}}
\newcommand{\ReNineNineAirDate}{Air date: Wednesday, 28th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReNineNineOnX}{\emph{Just-in-case and just-in-time as strategies for what to learn when.}}
\newcommand{\ReNineNineAbstract}{What has become obvious while focusing on the math and code of AIMA4e; needs, constraints, real goals, collapse into specialization; just-in-case (JIC) or bottom-up, and just-in-time (JIT) or top-down approaches to learning and doing; pinching knowledge by searching from opposing directions; evidence of math and code needs; remembering purposes.}


\newcommand{\ReOneZeroZeroTitle}{Re100: \emph{News of ChatGPT, Part 3}}
\newcommand{\ReOneZeroZeroAirDate}{Air date: Thursday, 29th Dec. 2022, 10:00 PM Eastern/US.}
\newcommand{\ReOneZeroZeroOnX}{\emph{An interpretation of ChatGPT's architecture.}}
\newcommand{\ReOneZeroZeroAbstract}{Language models, question answering, machine translation, captioning, summarization; formal vs. natural language, grammar and syntax; conditional probabilities of strings given strings; parameters; deep neural networks; ChatGPT's three steps; supervised policy, reward model, optimized policy using PPO to choose step size in gradient descent.}

\newcommand{\ReOneZeroOneTitle}{Re101: \emph{News of ChatGPT, Part 4}}
\newcommand{\ReOneZeroOneAirDate}{Air date: Friday, 30th Dec. 2022, 4:00 PM Eastern/US.}
\newcommand{\ReOneZeroOneOnX}{\emph{How ChatGPT crosses with the hypotheses.}}
\newcommand{\ReOneZeroOneAbstract}{More attempts to describe ChatGPT; maximizing its reward; intended uses; what it might tend to do, overall; new means, old ends; what it is `thinking'; dialogue as key; improving human search-and-find space and medical knowledge and information; OpenAI's whack-a-mole burden; the Chinese, Americans, left-leaners and right-leaners now to be attacked with mis- and dis-information; strategic search-and-find information now easier to get; our collective environment now contains new agents, the ChatGPTs; the technological `future' containing ChatGPT is now the `present' and `past'; smart people will benefit more; bad guys; wealth; wildcards; hackers; control of humans by words; change of the environment by ChatGPTs; motivation to control.}

\newcommand{\ReOneZeroTwoTitle}{Re102: \emph{AI For What}}
\newcommand{\ReOneZeroTwoAirDate}{Air date: Saturday, 31st Dec. 2022, 2:00 PM Eastern/US.}
\newcommand{\ReOneZeroTwoOnX}{\emph{Well-formed goals in the computer control game.}}
\newcommand{\ReOneZeroTwoAbstract}{Kurzweil and all that; our countdown clocks to 2029 and 2042; machines can learn whatever we can, probably; systems and papers to study; reasons to learn or pay attention to AI; the purpose of Retraice; a more formal represenation of the player state change problem; moonshots for 2023 and 2024.}


\newcommand{\ReOneZeroThreeTitle}{Re103: \emph{Dimensions of Intelligent Agents} (Day 1, AIMA4e Chpt. 1)}
\newcommand{\ReOneZeroThreeTitlesplit}{Re103: \emph{Dimensions of Intelligent Agents} \\(Day 1, AIMA4e Chpt. 1)}
\newcommand{\ReOneZeroThreeAirDate}{Air date: Sunday, 1st Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneZeroThreeOnX}{\emph{Adding fitness and truth to AIMA's dimensions, and considering `artificial flight'.}}
\newcommand{\ReOneZeroThreeAbstract}{Deciding vs. discovering what intelligence and AI are; Vico on knowledge and engineering; the spectrum view and the category view of intelligent agents; `artificial flight', birds and intelligence.}

\newcommand{\ReOneZeroFourTitle}{Re104: \emph{Agent Functions, Agent Programs, Task Environments} (Day 2, AIMA4e Chpt. 2)}
\newcommand{\ReOneZeroFourTitlesmall}{\small Re104: \emph{Agent Functions, Agent Programs, Task Environments} (Day 2, AIMA4e Chpt. 2)}
\newcommand{\ReOneZeroFourTitlesplit}{Re104: \emph{Agent Functions, Agent Programs, Task Environments} \\(Day 2, AIMA4e Chpt. 2)}
\newcommand{\ReOneZeroFourAirDate}{Air date: Monday, 2nd Jan. 2023, 2:00 PM Eastern/US.}
\newcommand{\ReOneZeroFourOnX}{\emph{Correcting the TABLE-DRIVEN-AGENT series and modeling agents and environments.}}
\newcommand{\ReOneZeroFourAbstract}{Agent functions (math) and agent programs (code); task environments as problems, agents as solutions; labeling artifacts as agents or not; the most interesting artifacts; the PEAS-OADESDU model of task environments; locating the performance measure; utility functions; software agents and their sensors and actuators; the relevant parts of the universe; AI literacy (autoracy?) vs. literacy, numeracy, coding literacy (coderacy?).}


\newcommand{\ReOneZeroFiveTitle}{Re105: \emph{Solve or Be Solved} (Day 3, AIMA4e Chpt. 3)}
\newcommand{\ReOneZeroFiveTitlesplit}{Re105: \emph{Solve or Be Solved} \\(Day 3, AIMA4e Chpt. 3)}
\newcommand{\ReOneZeroFiveAirDate}{Air date: Tuesday, 3rd Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneZeroFiveOnX}{\emph{The mechanical advantage of those who control AI engineers.}}
\newcommand{\ReOneZeroFiveAbstract}{The agent-environment boundary; environments to be solved by agents; AI-CS tools recent, vast; mechanical advantage in physics and AI; math vs. AI-CS; the enormous problem-solving advantage of those who control AI engineers.}


\newcommand{\ReOneZeroSixTitle}{Re106: \emph{Elitism, Culling, Coercion, Adversaries, Strategy} (Day 4, AIMA4e Chpt. 4)}
\newcommand{\ReOneZeroSixTitlesmall}{\small Re106: \emph{Elitism, Culling, Coercion, Adversaries, Strategy} (Day 4, AIMA4e Chpt. 4)}
\newcommand{\ReOneZeroSixTitlesplit}{Re106: \emph{Elitism, Culling, Coercion, Adversaries, Strategy} \\(Day 4, AIMA4e Chpt. 4)}
\newcommand{\ReOneZeroSixAirDate}{Air date: Wednesday, 4th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneZeroSixOnX}{\emph{Technical terms from loaded words.}}
\newcommand{\ReOneZeroSixAbstract}{Evolutionary algorithms and their techniques; sensorless agent problems and coercing environments; adversaries in online search; conditional plans as strategy in complex environments; Vallee, `Major Murphy', science, the price of information, counterespionage and AI.}



\newcommand{\ReOneZeroSevenTitle}{Re107: \emph{Three Kinds of AI (Day 5, AIMA4e Chpt. 5)}}
\newcommand{\ReOneZeroSevenTitlesplit}{Re107: \emph{Three Kinds of AI} \\(Day 5, AIMA4e Chpt. 5)}
\newcommand{\ReOneZeroSevenAirDate}{Air date: Thursday, 5th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneZeroSevenOnX}{\emph{War, peace and commerce AI in our multi-agent world.}}
\newcommand{\ReOneZeroSevenAbstract}{Considering multi-agent environments as economies, adversarial games, or merely nondeterministic; commerce, peace, war; Bostrom's `capacity building' and `strategic analysis'; adversary arguments; the computer control game; solving for mobilization and war.}

\newcommand{\ReOneZeroEightTitle}{Re108: \emph{Contributors and Controllers} (Day 6, AIMA4e Chpt. 6)}
\newcommand{\ReOneZeroEightTitlesplit}{Re108: \emph{Contributors and Controllers} \\(Day 6, AIMA4e Chpt. 6)}
\newcommand{\ReOneZeroEightAirDate}{Air date: Friday, 6th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneZeroEightOnX}{\emph{A subdivision within the players of the computer control game.}}
\newcommand{\ReOneZeroEightAbstract}{CSPs and factored vs. atomic representations; war in Re107; Re69's citation date; the many applications of CSPs, and contributors; contributors and controllers in computer control; nation states, sub-states, companies; politicians, spooks, military, police; shareholders, directors, executives; engineers, professors; hackers.}


\newcommand{\ReOneZeroNineTitle}{Re109: \emph{TikTok (app), Tik-Tok (novel), and Low-Power Mode} (Day 7, AIMA4e Chpt. 7)}
\newcommand{\ReOneZeroNineTitlesmall}{\small Re109: \emph{TikTok (app), Tik-Tok (novel), and Low-Power Mode} (Day 7, AIMA4e Chpt. 7)}
\newcommand{\ReOneZeroNineTitlesplit}{Re109: \emph{TikTok (app), Tik-Tok (novel), and Low-Power Mode} \\(Day 7, AIMA4e Chpt. 7)}
\newcommand{\ReOneZeroNineAirDate}{Air date: Saturday, 7th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneZeroNineOnX}{\emph{An observation of AI in action (TikTok), a decision (Low-Power Mode), and a coincidence (Tik-Tok).}}
\newcommand{\ReOneZeroNineAbstract}{TikTok as addictive spying tool; Tik-Tok, the novel; changes in technology vs. lack of changes in human wants and needs; creeping totalitarianism, illiberty, war, climate change, Artilect War, superintelligence; the gorilla problem; making a living, making a difference; AIMA4e, Retraice, audience; low-power mode.}


\newcommand{\ReOneOneZeroTitle}{Re110: \emph{TikTok for Addicting the World's Kids}}
\newcommand{\ReOneOneZeroAirDate}{Air date: Sunday, 8th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneOneZeroOnX}{\emph{Tristan Harris's analysis of China's TikTok vs. the exported version.}}
\newcommand{\ReOneOneZeroAbstract}{Tristan Harris on TikTok; spinach TikTok for Chinese kids, opium for everyone else; the Opium Wars and the `Century of Humiliation'; TikTok content and time limits for Chinese kids; Netflix on the attention economy vs. sleep; Russia and China trying to radicalize U.S. veterans via social media; war and civil war.}

\newcommand{\ReOneOneOneTitle}{Re111: \emph{AI and the Gorilla Problem}}
\newcommand{\ReOneOneOneAirDate}{Air date: Monday, 9th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneOneOneOnX}{\emph{Russell and Norvig say it's natural to worry that AI will destroy us, and that the solution is good design that preserves our control.}}
\newcommand{\ReOneOneOneAbstract}{Our unlucky evolutionary siblings, the gorillas; humans the next gorillas; giving up the benefits of AI; the standard model and the human compatible model; design implications of human compatibility; the difficulty of human preferences.}


\newcommand{\ReOneOneTwoTitle}{Re112: \emph{The Attention Hazard and The Attention (Distraction) Economy}}
\newcommand{\ReOneOneTwoTitlesplit}{Re112: \emph{The Attention Hazard \\and The Attention (Distraction) Economy}}
\newcommand{\ReOneOneTwoAirDate}{Air date: Tuesday, 10th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneOneTwoOnX}{\emph{Drawing attention to dangerous information can increase risk, but the attention economy tends to draw attention toward amusement.}}
\newcommand{\ReOneOneTwoAbstract}{Information hazards; formats include data, idea, attention, template, `signaling' and `evocation'; increasing the number of information locations; adversaries, agents, search, heuristics; the dilemma of attention; suppressing secrets; the Streisand effect; the attention economy as elite `solution'; Liu's `wall facers'.}


\newcommand{\ReOneOneThreeTitle}{Re113: \emph{Uncertainty, Fear and Consent} (Technological Danger, Part 1)}
\newcommand{\ReOneOneThreeTitlesplit}{Re113: \emph{Uncertainty, Fear and Consent} \\(Technological Danger, Part 1)}
\newcommand{\ReOneOneThreeAirDate}{Air date: Wednesday, 11th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneOneThreeOnX}{\emph{Beliefs, and the feelings they cause, determine what chances we take; but possibilities don't care about our beliefs.}}
\newcommand{\ReOneOneThreeAbstract}{A prediction about safety, security and freedom; decisions about two problems of life and the problem of death; uncertainty, history, genes and survival machines; technology to control the environment of technology; beliefs and feelings; taking chances; prerequisites for action; imagining possibilities; beliefs that do or don't lead to consent; policing, governance and motivations.}



\newcommand{\ReOneOneFourTitle}{Re114: \emph{Visions of Loss} (Technological Danger, Part 2)}
\newcommand{\ReOneOneFourTitlesplit}{Re114: \emph{Visions of Loss} \\(Technological Danger, Part 2)}
\newcommand{\ReOneOneFourAirDate}{Air date: Thursday, 12th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneOneFourOnX}{\emph{Human loss of freedom by deference to authority, dependency on machines, and delegation of defense.}}
\newcommand{\ReOneOneFourAbstract}{Wiener: freedom of thought and opinion, and communication, as vital; Russell: diet, injections and injunctions in the future; Horesh: technological behavior modification in the present; terrorist Kaczynski: if AI succeeds, we'll have machine control or elite control, but no freedom; Bostrom: wearable surveillance devices and power in the hands of a very few as solution.}

\newcommand{\ReOneOneFiveTitle}{Re115: \emph{Technological Progress, Defined} (Technological Danger, Part 3)}
\newcommand{\ReOneOneFiveTitlesplit}{Re115: \emph{Technological Progress, Defined} \\(Technological Danger, Part 3)}
\newcommand{\ReOneOneFiveAirDate}{Air date: Friday, 13th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneOneFiveOnX}{\emph{How we would decide, given predictions, whether to risk continued technological advance.}}
\newcommand{\ReOneOneFiveAbstract}{Danger, decisions, advancing and progress; control over the environment and `we'; complex, inconsistent and conflicting human preferences; `coherent extrapolated volition' (CEV); divergence, winners and losers; the lesser value of humans who disagree; better and worse problems; predicting progress and observing progress; learning from predicting progress.}


\newcommand{\ReOneOneSixTitle}{Re116: \emph{When Does the Bad Thing Happen? (Technological Danger, Part 4)}}
\newcommand{\ReOneOneSixTitlesplit}{Re116: \emph{When Does the Bad Thing Happen?} \\(Technological Danger, Part 4)}
\newcommand{\ReOneOneSixAirDate}{Air date: Saturday, 14th Jan. 2023, 10:00 PM Eastern/US.}
\newcommand{\ReOneOneSixOnX}{\emph{Agreements about reality in technological progress.}}
\newcommand{\ReOneOneSixAbstract}{Basic questions; a chain reaction of philosophy; deciding what is and isn't in the world; agreeing with others in order to achieve sharing; other concerns compete with sharing and prevent agreement; the need for agreement increasing.}

% ....abstracts done above
%%%% temp:







\newcommand{\ReOneOneSevenTitle}{Re117: \emph{Purpose and Resources}}
\newcommand{\ReOneOneSevenAirDate}{Air date: Thursday, 22nd Jun. 2023, 4:30 PM Eastern/US.}
\newcommand{\ReOneOneSevenOnX}{\emph{What Retraice is trying to do, and how.}}
\newcommand{\ReOneOneSevenAbstract}{nnnnnooooooottttttttttttSetttttt}



\newcommand{\MaTwoFourTitle}{Ma24: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoFourAirDate}{Air date: Friday, 23rd Jun. 2023, nnnnnooooooottttttttttttSetttttt Eastern/US.}
\newcommand{\MaTwoFourOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoFourAbstract}{nnnnnooooooottttttttttttSetttttt}



\newcommand{\MaTwoFiveTitle}{Ma25: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoFiveAirDate}{Air date: Saturday, 24th Jun. 2023, nnnnnooooooottttttttttttSetttttt Eastern/US.}
\newcommand{\MaTwoFiveOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoFiveAbstract}{nnnnnooooooottttttttttttSetttttt}



\newcommand{\MaTwoSixTitle}{Ma26: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoSixAirDate}{Air date: Sunday, 25th Jun. 2023, nnnnnooooooottttttttttttSetttttt Eastern/US.}
\newcommand{\MaTwoSixOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoSixAbstract}{nnnnnooooooottttttttttttSetttttt}



\newcommand{\MaTwoSevenTitle}{Ma27: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoSevenAirDate}{Air date: Monday, 26th Jun. 2023, nnnnnooooooottttttttttttSetttttt Eastern/US.}
\newcommand{\MaTwoSevenOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoSevenAbstract}{nnnnnooooooottttttttttttSetttttt}



\newcommand{\MaTwoThreeTitle}{Ma23: \emph{Update – Making Things Work}}
\newcommand{\MaTwoThreeAirDate}{Air date: 2023-06-15 Thu 22:00 Eastern/US.}
\newcommand{\MaTwoThreeOnX}{\emph{A new approach following Low-Power Mode (Re109--Re116) and Power-Down (Jan--Jun 2023).}}
\newcommand{\MaTwoThreeAbstract}{nnnnnooooooottttttttttttSetttttt}



\newcommand{\MaTwoEightTitle}{Ma28: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoEightAirDate}{Air date: nnnnnooooooottttttttttttSetttttt Eastern/US.}
\newcommand{\MaTwoEightOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoEightAbstract}{nnnnnooooooottttttttttttSetttttt}




\newcommand{\MaTwoNineTitle}{Ma29: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoNineAirDate}{Air date: nnnnnooooooottttttttttttSetttttt Eastern/US.}
\newcommand{\MaTwoNineOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaTwoNineAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeZeroTitle}{Ma30: \emph{You're Competing for Everything}}
\newcommand{\MaThreeZeroAirDate}{Air date: 2023-11-20 Mon 11:00 Eastern/US.}
\newcommand{\MaThreeZeroOnX}{\emph{Time, space, ideas, stuff and people all go to those who play hard.}}
\newcommand{\MaThreeZeroAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeOneTitle}{Ma31: \emph{Some Personal Experience With Delusions}}
\newcommand{\MaThreeOneAirDate}{Air date: 2023-11-21 Tue 13:00 Eastern/US.}
\newcommand{\MaThreeOneOnX}{\emph{Wishful thinking leads to disappointment and, sometimes, an interst in false beliefs.}}
\newcommand{\MaThreeOneAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeTwoTitle}{Ma32: \emph{Venting}}
\newcommand{\MaThreeTwoAirDate}{Air date: 2023-11-22 Wed 11:00 Eastern/US.}
\newcommand{\MaThreeTwoOnX}{\emph{I'm wound up.}}
\newcommand{\MaThreeTwoAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeThreeTitle}{Ma33: \emph{Follow Your Shoulders}}
\newcommand{\MaThreeThreeAirDate}{Air date: 2023-11-23 Thu 10:00 Eastern/US.}
\newcommand{\MaThreeThreeOnX}{\emph{How to decide when to walk, jog, run and sprint—and toward what.}}
\newcommand{\MaThreeThreeAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeFourTitle}{Ma34: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeFourAirDate}{Air date: 2023-11-24 Fri 10:00 Eastern/US.}
\newcommand{\MaThreeFourOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeFourAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeFiveTitle}{Ma35: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeFiveAirDate}{Air date: 2023-11-25 Sat 05:00 Eastern/US.}
\newcommand{\MaThreeFiveOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeFiveAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeSixTitle}{Ma36: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeSixAirDate}{Air date: 2023-11-26 Sun 04:00 Eastern/US.}
\newcommand{\MaThreeSixOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeSixAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeSevenTitle}{Ma37: \emph{Focus, Faster}}
\newcommand{\MaThreeSevenAirDate}{Air date: 2023-11-27 Mon 04:00 Eastern/US.}
\newcommand{\MaThreeSevenOnX}{\emph{I have one job right now: clear the backlog.}}
\newcommand{\MaThreeSevenAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeEightTitle}{Ma38: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeEightAirDate}{Air date: 2023-11-28 Tue 04:00 Eastern/US.}
\newcommand{\MaThreeEightOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeEightAbstract}{nnnnooooooottttttttttttSetttttt}



\newcommand{\MaThreeNineTitle}{Ma39: \emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeNineAirDate}{Air date: 2023-11-29 Wed 04:00 Eastern/US.}
\newcommand{\MaThreeNineOnX}{\emph{nnnnnooooooottttttttttttSetttttt}}
\newcommand{\MaThreeNineAbstract}{nnnnooooooottttttttttttSetttttt}
